\chapter{Crows And Hares}

WHEN I ANNOUNCED, at a swish cocktail party, that I had visited an esoteric incensey fairy airhead goddess gift shop, it was assumed by all and sundry that I had made a  mistake, believing it, in myopic confusion, to be a tobacconist's. Well, let me state loudly and clearly that I marched into what I well knew to be a shop full of woohoowoo with due deliberation. And I did so, dear readers, purely for your benefit, for I was researching the arcane and eldritch powers of crows and hares.

Rustic persons have long been aware of the magical and oracular nature of crows and hares, harbouring knowledge lost to the typical urban Hooting Yard reader. That is why I get so many letters from people who somehow expect me to be privy to ancient countryside lore, people who are too timid, or proud, to set foot themselves in esoteric incensey fairy airhead goddess gift shops. By last week I had grown so fed up with the constant stream of crow- and hare-related missives that I betook myself to an appropriate emporium.

Those of you wallowing in the slops of ignorance need to know, first of all, that a crow is a type of bird and a hare is very similar to a rabbit. Try not to get them mixed up. Memorising one of Pontius Wilmslow's so-called 'animal mnemonics' may be of help:

\emph{The crow is black, and flies across the sky. The hare is brown and gambols in the meadow.}

There. Repeat that a few hundred times, until it is lodged securely in the blob of your brain, and you won't go far wrong.

In order to exploit the oracular nature of your personal crow and/or hare spirit guide, you need a few pebbles and some cards. For the latter, the best thing to do is to obtain an old pack of playing cards, steep them one by one in bleach, and then scribble runic devices upon them with a magic marker pen. If you are not sure what a runic device looks like, just scribble any old how, on one card after another, imagining perhaps that you are a grunting primitive caveman trying ignorantly to assuage a psychotic and enraged cave-god. All that really matters is that you can tell the difference between one card and another. When you've done that, get some pebbles, scrub them clean of muck and mud, and scribble the same runic devices upon them. Divide the cards and pebbles into two sets, and chuck one in to a cardboard box marked 'Crow' and the other into a cardboard box marked 'Hare'. Decorate the cardboard boxes with winsome starry moony emblems and tie ribbons around them. Knot the ribbons with knots you have learned to tie from \emph{Poopy Klammberg's Book Of Magick Knots}, available from your local esoteric incensey fairy airhead goddess gift shop. Yes, I'm afraid you're going to have to step through its door sooner or later. I did, and I have lived to tell the tale.

You will be surprised how quickly you will learn whether it is propitious to consult your crow oracle or your hare oracle, or both, or neither, during particular weather conditions, or to answer specific questions. Let us say you wake up on a freezing cold morning, with the wind coming in from the west and a hailstorm brewing. Uppermost in your mind, after your nightmares, is the question of precisely how much time will pass before David Blunkett is again attacked by a cow. Instinct will tell you whether this is a matter for the crow or the hare. Taking the appropriate box from its plinth upon your homemade sacred shrine, cast a handful of pebbles upon the rug, and then deal out some of the cards. Oh, don't forget, before doing so, to cleanse both pebbles and cards by wafting incense over them and babbling a mantra. The combination of the runes on the cast pebbles and the dealt cards, and their disposition upon the rug, will hold the answer to your question. Be warned that it is not immediately obvious. In fact, it may be quite beyond your wit to understand it. In such cases, take a snapshot of the rug, with the cards and pebbles in clear view and sharp focus, and send it to me. I will tell you what it all means, for I have communed with both the crow spirits and the hare spirits, and there is an invisible star on my forehead, and straw in my hair.

