\chapter{Little Ruskin, Episode One}

\begin{quotation}
`I was extremely fond of digging holes, but that form of gardening was not allowed.' 

-- John Ruskin, \emph{Praeterita, Volume I} (1885/6)
\end{quotation}

LOOK, CHILDREN, THERE goes little Ruskin, marching up the path with his spade over his shoulder! But who is this come a-lolloping towards him? It is Mr Snippage, the kindly old gardener, Mr Snippage who leaves ants'-nests undisturbed so little Ruskin can investigate them with his already piercing observational skills.

'What ho!' says Mr Snippage, 'Now what would you be about, little Ruskin, with that spade over your shoulder?'

'I am going to dig holes here in our Herne Hill garden, Mr Snippage. I am extremely fond of digging holes,' replies the infant.

'Ho ho ho,' laughs Mr Snippage, 'I knows you are, little Ruskin. But I don't think your Ma takes too kindly to all your hole-digging, does she now?'

Little Ruskin blushes. Last summer he had dug so many holes the house on the hill had been at risk of subsidence. That is why he plans to dig this year's holes at the farthest end of the garden. But he can find no words to say in reply to Mr Snippage.

'I know your Ma gets you a-Bible reading every morning,' continues the gardener, 'And I know she added an eleventh commandment, didn't she?'

Little Ruskin nods.

'Thou shalt not dig holes in the garden,' quotes Mr Snippage, 'And she didn't mean the garden of Eden, did she now?'

Little Ruskin tosses his spade aside and begins to sob.

'There, there,' says Mr Snippage, mussing little Ruskin's carefully-combed hair, 'Let's you and me see if we can't find an ants'-nest to study.'

And he takes little Ruskin by the hand and leads him off towards where he knows there will be an ants'-nest or two.

Ma Ruskin looks on at the scene from the drawing-room window. She clutches her doctored Bible to her bosom and offers up a prayer of thanks that the kindly old gardener has turned little Ruskin away from the path of sin.
