\chapter{Pelican}

THERE WERE PELICANS I hungered to see. Those huge, scooping bills, gulping down fish small and large, from sprats to trout. I felt an affinity with pelicans, even though the only pelicans I had ever seen were illustrations in reference books, \emph{The A-Z Of Seabirds} and \emph{The Life Of Pelicans}, for example. Was it because I could imagine opening my gullet and swallowing fish whole? It may have been. It is true my diet consists mostly of fish, bream and plaice, mackerel and eels. Especially eels. I prefer to eat them whole, and raw, and still alive. Into my maw goes the eel, head first, terrified I expect, but then that is the way of nature, creatures feeding upon each other. If I am ever swallowed whole by some beast bigger than me, I will not complain. I will be scared stupid, but nestling within the fear of an imminent doom will be a sense that this is the way the world works. I have never seen myself as a nibbler, a mouse, say, at a piece of cheese, or a beaver gnawing upon a log. There is that in me which is attracted by the engorging of a living, wriggling, squirming, sea-salt smeared piscine creature, all in one go. I expect I get it from my parents, Roman Catholics who dutifully stuck to fish on Fridays and had terrible table manners. Pa would nip out to the fishmonger's and bring home a wrapped package of something that had been swimming innocently but a couple of hours before, and smear it with sauce and sprinkle it with salt and pepper and cut it up with a knife and fork and ration it out. Greedy me, I always wanted the whole thing, I never wanted to share, and as soon as I was grown and no longer dependent upon my Pa for my fish I would indulge myself, from Saturday to Thursday as well as on Fridays. Haddock, plaice, and those yummy yummy eels, I feasted on them all. When I realised I wanted to eat them alive I stopped going to the fishmonger's and bought myself a fishing rod and headed for the riverbank, I even got myself wading boots, and I cast my line in the muddy river and discovered a knack for fishing. It was as if they came to me, biting my bait, offering themselves, wanting to be eaten up and serve my appetite. And they did, oh they did, in their teeming thousands, even the swivelbacks and the gunnies and the ling. I have never seen a pelican, but when I preen before the mirror of an evening it is a human pelican I see, one whose stomach is stuffed with fish, a human pelican missing that mighty bill but otherwise just as ravenous, and just as elegant.