\chapter{An Advertisment For Chumpots}

CHUMPOT'S PATENT RAREFIED Pigfat 'n' Sourdough Paste comes in handy tubes. Spread thickly on a digestive biscuit, or between two slices of sliced-up solidified milk sludge, it makes for a perfect picnic snack.

You will well know, if ever you have been held responsible for the packing of a picnic hamper, the difficulty of picking the appropriate picnic snacks. How common it is, to be sat in a meadow, pipe clenched in your teeth, moustache bristling, to be lambasted by your fellow picnickers as the picnic hamper is unpacked and harsh words are said about, say, the sausages or the unsliced, unsolidified milk sludge. Many an idyllic picnic has been destroyed before it has even properly begun because of hamper-contents fury. Many meadows have resounded with unseemly imprecations. Many moustache-ends have been tweaked with spiteful tugs by the fingers of furious picnickers reaching across the picnic rug to assault the hamper packer. It is a sorry state of affairs, but one which Chumpot's aims to make a thing of the past. Our pastes are beyond reproach.

We have been manufacturing pastes, in tubs and tubes, for over a century, from our pasteworks in Pointy Town. Old Pa Chumpot, who founded the firm, and whose moustache was as magnificent an example of the walrus variety as has ever been grown in this town, made it his business to end picnic unpleasantness good and proper. It is easy to chuckle at those early promotional leaflets, with their clunky slogans such as 'There will be no more unwarranted tweaking of moustaches at picnics when you pack Chumpot's pastes in your picnic hamper', but they bespeak a great moral purpose. It was a time when meadows were loud with the din of moustachioed men wearing boaters, pipes clenched between their teeth, venting their fury at the choice of snacks packed into their picnic hampers. Bebonneted ladies blushed and held their dainty hands over their ears and, in some cases, swooned. Into this maelstrom stepped Old Pa Chumpot, with pastes specifically designed to bring due decorum to our meadows. For more than a hundred years now, the firm that still bears his name has continued to manufacture exciting and toothsome pastes, usually quite edible, for use at picnics. We are proud to do so.