\chapter{Those Wednesday Potato Nights}

DOBSON ADORED WEDNESDAY potato nights. It would be no exaggeration to say he was besotted with them. He would fairly skip along the twilit lanes to the appointed field, where he would join his many, many equally potatotastic pals as they

\emph{Hang on. I was always under the impression that Dobson was a solitary sort, even a recluse, sitting alone at his escritoire, with only Marigold Chew for company, and she in a different room. This is the first I've heard of 'many, many pals'.}

Ah. Well, Dobson was indeed an immensely popular figure, with friends of all shapes and sizes scattered in bailiwicks near and far. What one has to remember is that most of the time he shunned them. But they were a forgiving lot, entranced, perhaps, by the honour of being counted among the so-called 'pals of the pamphleteer'. And so, at twilight on Wednesday potato nights, they gathered in a field, a happy band, and

\emph{This all seems a bit dubious to me. One minute Dobson is shunning his friends, as we might expect of him, and now he is skipping along a lane with them, presumably with an idiot grin on his face and flowers in his hair.}

Your presumptions are wrong, whoever you are. A man - even a pamphleteer - can be happy without sporting an 'idiot grin'. And flowers in the hair is your own invention. There is nothing to suggest Dobson adopted such a hippy head decoration. As for shuttling back and forth between the enshunment and the unshunment of his pals, how could it be otherwise if we regard Dobson as fully human, with all the flaws and inconsistencies and non-hippy headgear choices of an everyman? Now, gathering in the field, armed with their potatoes and camping-gaz stoves and flasks of water, the enthusiasts watched the last glimmers of sunlight vanish below the horizon, and ignited their torches of petrol-soaked rags tied to the ends of sticks. Over yonder, sprites disported themselves in the fug above the eerie marsh.

\emph{What?}

Over yonder, sprites disported themselves in the

\emph{Yes, I heard what you said. Surely a fug is something you get in a confined space, like the fug of smoke in the saloon bar of the Cow \& Pins in the days before the smoking ban. You wouldn't get a fug over a marsh, however eerie, unless of course these are cigar-smoking sprites you're talking about.}

Pipe-smoking sprites, actually. And because there is no wind on Wednesday potato nights, not even the hint of a breeze, the air above the eerie marsh is still, and the smoke from the sprites' pipes hangs there, eerily, in a fug. And Dobson and all his many pals stand in their field, torches lit, peering at the marsh-fug, as if transfixed, before setting about their potato business. They pour water from their flasks into pots, and they light the camping-gaz

\emph{You didn't mention anything about pots before, when you listed what they brought with them. Potatoes and camping-gaz stoves and flasks, you said. In fact, you didn't say anything about the torches of petrol-soaked rags tied to the ends of sticks, until they lit them. And you haven't explained what they lit them with. Matches? Zippo lighters? I like detail, and you are not providing it. Would it not be better, at the outset, to give us a comprehensive list of all the items these people were carrying along the twilit lanes towards the fields, on Wednesday potato nights?}

You want a comprehensive list?

\emph{That would be excellent! A catalogue, perhaps, with a description of each item, and a catalogue number, and price, and an online shopping basket and checkout, so that if I wanted to I could use my Hooting Yardcard to actually buy the things. You would have to add pictures too, of course, in colour.}

Well, that would take

\emph{And while you're about it, a supplement to the catalogue, inserted at the end, with similar details of the marsh sprites' pipes and pipe-smoking paraphernalia, for there are always various bits and bobs a pipeist needs to enjoy a proper pipe-smoking experience, like pipe-cleaners, for instance. And even though it is just a supplement, not part of the main catalogue per se, it should have a similar level of detail, with photographs of all the pipe-cleaners and so on, in colour.}

That is rather a lot of work.

\emph{Yes, I grant you that. But has it not occurred to you that this is the kind of thing your readers are crying out for? It's all very well blathering on about a pamphleteer and his supposed unshunned pals boiling potatoes in a field in the night, but we want to be able to recreate these scenes in the comfort of our own community hub fenced-off frolicking compounds, and we need the kit to be able to do so. Think of the money you could make!}

Well, I suppose the main catalogue wouldn't be too much of a problem. Time-consuming and a bit finicky, but I could do it. Whereas the supplement would be much more difficult. Have you ever tried to take a photograph of a pipeist sprite above an eerie marsh?

\emph{I can't say that I have.}

I would need a spirit camera. Ordinary cameras would be worse than useless, all you would see would be a grey blur.

\emph{A blur will do, I'm not fussy. I can study the photographs using my etheric eerie marsh spriteoscope. Buy one, get one free at Hubermann's.}

So in essence, all your interruptions have been leading up to a blatant advertisement for that confounded department store? That's despicable.

\emph{Maybe so, but as you know, Hubermann's is a byword for utter gorgeousness.}